A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-09-19 manuscript/manuscript.tex
Updates to ITHIM manuscript #1
I included the figure of mean travel time by mode, region and age-sex stratum.  I also added citations for the data and worked on the Regional Analysis section

\title[\package{}]{\package{}: an \R{} package for implemetation of
  the ITHIM model}
\author[Younkin \textit{et~al}]{Samuel G. Younkin$^{1}$,
  Jason Vargo$^{1}$\footnote{to whom correspondence should be addressed},
  $\ldots$
  \ and Jonathan Patz$^{1}$}
\address{$^{1}$Global Health Institute\\
University of Wisconsin{\textendash}Madison, Madison, WI USA\\
}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

@@

\col[blue]{\textit{
    The time spent walking or cycling, i.e., active transport time, is
modeled as a log-normal random variable with means defined for each
age-sex stratum.  The non-travel-related physical activity is also
modeled as log-normal with stratum-specific means.  Estimates for
non-travel-related physical activity are diffiuclt.  We used the
American Time Use Survey data to estimate the relative means for each
of the age-sex strata.  We then treat the mean of the referent group
as a variable and compute results over a grid of values for this
variable.  See Figure \ref{dalyFigure}.
}}

@@

\col[blue]{\textit{
We chose to model road injuries in a more simplifed manner than the
authors of ITHIM.  The original ITHIM requires information about the
transportational infrastructure that cannot be accurately modeled on a
regional level, and is more well-suited to say a collection of
counties as a case study. \cite{maizlish2013}  We use the overall percent
of travel by walking and road fatalities per U.S. metropolitan area to
estimate road fatalaties in U.S. metropolitan areas given the percent
of travel by walking. \cite{UWTechReport}
}}

\col[blue]{\textit{
We need to estimate the increase/decrease in road injuries/fatalaties
nation-wide as walking/cycling time increases.  We need a relative
risk of road fatalaty as a function of active transport time...
}}

@@

\col[blue]{\textit{
    Can we model the decrease in \pEm{2.5} nationally as a function of
decrease in driving time?  The original plan was to use a baseline
value for \pEm{2.5} and a linear relationship bewteen change in
\pEm{2.5} and change in \vmt{}.
}}

@@

\section{U.S. Metro-Regional Analysis}
\col[blue]{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur
adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore
magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
ullamco laboris nisi ut aliquip ex ea commodo consequat.}

\subsection{Data Sources}

\col[red]{Lorem ipsum dolor sit amet, consectetur adipisicing)) elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur
adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore
magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
ullamco laboris nisi ut aliquip ex ea commodo consequat.}

@@

\section*{Acknowledgment}
\paragraph{Funding\textcolon} SGY is supported by$\ldots$ , JV, JP, $\ldots$

>>>>

\title[\package{}]{A comparative risk assesment of U.S. regional
  active transport using the ITHIM model}
\author[Younkin \textit{et~al}]{Samuel G. Younkin$^{1}$,
  Jason Vargo$^{1}$\footnote{to whom correspondence should be addressed},
  $\ldots$
  \ and Jonathan Patz$^{1}$}
\address{$^{1}$Global Health Institute\\
University of Wisconsin{\textendash}Madison, Madison, WI USA\\
}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

@@

\col[blue]{\textit{The time spent walking or cycling, i.e., active
    transport time, is modeled as a log-normal random variable with
    means defined for each age-sex stratum.  The non-travel-related
    physical activity is also modeled as log-normal with
    stratum-specific means.}}

@@

\col[red]{\textit{
We chose to model road injuries in a more simplifed manner than the
authors of ITHIM.  The original ITHIM requires information about the
transportational infrastructure that cannot be accurately modeled on a
regional level, and is more well-suited to say a collection of
counties as a case study. \cite{maizlish2013}  We use the overall percent
of travel by walking and road fatalities per U.S. metropolitan area to
estimate road fatalaties in U.S. metropolitan areas given the percent
of travel by walking. \cite{UWTechReport}
}}

\col[red]{\textit{
We need to estimate the increase/decrease in road injuries/fatalaties
nation-wide as walking/cycling time increases.  We need a relative
risk of road fatalaty as a function of active transport time...
}}

@@

\col[red]{\textit{
    Can we model the decrease in \pEm{2.5} nationally as a function of
decrease in driving time?  The original plan was to use a baseline
value for \pEm{2.5} and a linear relationship bewteen change in
\pEm{2.5} and change in \vmt{}.
}}

@@

\section{U.S. Metro-Regional Analysis}

\begin{figure}[t]
    \centerline{\includegraphics[width=0.4\textwidth]{./figures/fig3}}
    \caption{Foo}\label{meanMatrices}
\end{figure}

\col[blue]{\begin{itemize}
\item We used the National Household Transportation Survey \cite{NHTS} to
  estimate the mean walk and cycle times for individuals that live in
  metropolitan areas ($\textrm{DAYV2PUB.MSA} \in (1,2,\ldots,5)$ which
  corresponds to individuals whose homes are in an MSA or cMSA)
  \bi\item Data quality issues along with assumptions about travel speed
created mirky data.  The median values of trip time were used to avoid
undue influence by outliers.\ei
\item We then divided these into the 10 regions of the U.S. defined by
  the Department of Health and Human Services (HH1-10)
\item Using only the active transport component of the ITHIM model we
  ran comparative analyses for each of the ten regions, using the
  national averages as the baseline.
\item We used data from the American Time Use Survey \cite{ATUS} to
  estimate the relative means for each of the age-sex strata.  We then
  treat the mean of the referent group as a variable and compute
  results over a grid of values for this variable.  See Figure
  \ref{dalyFigure}.
\item Values for DALYs were found using the CDC Wonder database \cite{CDCWonder}
\end{itemize}}

@@

\section*{Acknowledgment}
\paragraph{Funding\textcolon} \col[red]{SGY is supported by$\ldots$ , JV, JP, $\ldots$}
